Author disambiguation of large-scale semi-labeled collections of scientific articles

### 2015-08-20 paper.tex
save

In this
framework, author disambiguation can be stated as the problem of
finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of ${\cal S}$ such
that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$ for all $i \neq
j$, and where subsets $c_i$, or clusters, each corresponds to the set of all
signatures belonging to the same individual $a_i$. Alternatively, the set
${\cal A}$ may remain (possibly partially) unknown, such that author
disambiguation boils down to finding a partition ${\cal C}$ where
subsets $c_i$  each corresponds to the set of all signatures from a same
individual (without knowing who). Finally, in the case of partially annotated databases as studied in
this work, the setting extends with the partial knowledge $\bar{{\cal C}} = \{ \bar{c_0}, ..., \bar{c_{M-1}} \}$ of ${\cal C}$,
such that $\bar{c_i} \subseteq c_i$, with $\bar{c_i}$ possibly empty.
Or put otherwise, the setting extends with the knowledge that all signatures
$s \in \bar{c_i}$ belong to author $a_i$.

@@

>>>>

In this
framework, author disambiguation can be stated as the problem of
finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of ${\cal S}$ such
that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$ for all $i \neq
j$, and where subsets $c_i$, or clusters, each corresponds to the set of all
signatures belonging to the same individual $a_i$. Alternatively, the set
${\cal A}$ may remain (possibly partially) unknown, such that author
disambiguation boils down to finding a partition ${\cal C}$ where
subsets $c_i$  each corresponds to the set of all signatures from a same
individual (without knowing who). Finally, in the case of partially annotated databases as studied in
this work, the setting extends with the partial knowledge $\bar{{\cal C}} = \{ \bar{c_0}, ..., \bar{c_{M-1}} \}$ of ${\cal C}$,
such that $\bar{c_i} \subseteq c_i$, with $\bar{c_i}$ possibly empty.
Or put otherwise, the setting extends with the knowledge that all signatures
$s \in \bar{c_i}$ belong to the same author.

@@

\glnote{Notations should be improved and be made more explicit}
